Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-07-03 Scripts/Initial_Analysis.Rmd

EstPropChange <- function(taxon_key,
                          year,
                          hist_y,
                          data_type = "Catch",
                          ensemble_list, # expects a list of ensembles to averrage by
                          path,
                          neighbours){

  # Loads species data for all ensembles
  Spp_Dist <- bind_rows(
    lapply(
      ensemble_list,
      dbem_import,
      taxon_key = taxon_key,
      year = year,
      data_type = data_type,
      path = path
    )
  )

@@

  # Save Result
  name <- paste("proportion_",taxon_key,".csv",sep="")
  path_name <- paste(result_path,"Proportion/",name, sep="")

>>>>

EstPropChange <- function(taxon_key,
                          year,
                          hist_y = 2005,
                          data_type = "Catch",
                          ensemble_list, # expects a list of ensembles to averrage by
                          path,
                          neighbours){

  # Loads species data for all ensembles
  Spp_Dist <- bind_rows(
    lapply(
      ensemble_list,
      read_dbem_ens,
      taxon_key = taxon_key,
      year = year,
      data_type = data_type,
       model = "GFDL",
      rcp = "85",
      path = "NA",
      my_path = F
    )
  )

@@

  # Save Result
  name <- paste("proportion_",taxon_key,".csv",sep="")
  path_name <- paste(my_path("R",extra_path = "Proportion_n"),name,sep= "")
